An Efficient E-field Parallel Imaging Calibration Algorithm for Next-Generation Radio Telescopes

### 2015-10-13 cal_demo/ms.tex
initial commit of cal paper, moving shared files up one directory

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[E-field Parallel Imaging Correlator]{A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Thyagarajan et al.]{
Nithyanandan Thyagarajan,$^{1}$\thanks{E-mail: t\_nithyanandan@asu.edu}
Adam P. Beardsley,$^{1}$
Judd D. Bowman$^{1}$
\newauthor
and Miguel F. Morales$^{2}$
\\
% List of institutions
$^{1}$Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA\\
$^{2}$University of Washington, Department of Physics, Seattle, WA 98195, USA\\
}

@@

Motivate MOFF from a technical and scientific standpoint. Refer to \citet{del07,mor09,mor11}.

@@

Refresh the math equivalence between MOFF and FX.

\section{Software Implementation}

Discuss implementation and make code available for public.

Calibration

@@

Show examples using simulations

Discuss PSF differences due to slight differences arising out of gridding

Apply it on LWA data

\section{Analysis and Feasibility}
\subsection{Scaling Relations: MOFF vs. FX}
\subsection{Scaling Up}
\subsection{Case Study}
% \subsection{Figures and tables}

@@

\bibliographystyle{mnras}
\bibliography{epic} % if your bibtex file is called example.bib

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{../mnras}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[E-field Parallel Imaging Calibration]{An Efficient E-field Parallel Imaging Calibration Algorithm for Next-Generation Radio Telescopes}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Beardsley et al.]{
Adam P. Beardsley,$^{1}$\thanks{E-mail: Adam.Beardsley@asu.edu}
Nithyanandan Thyagarajan,$^{1}$
Judd D. Bowman$^{1}$
\newauthor
and Miguel F. Morales$^{2}$
\\
% List of institutions
$^{1}$Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA\\
$^{2}$University of Washington, Department of Physics, Seattle, WA 98195, USA\\
}

@@

Motivate problem of calibrating direct imagers. Reference Nithyas paper. \citep{mor11}

@@

Introduce notation, describe measurement equation.

\section{Simulation}

Describe simulation

@@

Connect to either cramer-rao or FX solutions in some way

% \subsection{Figures and tables}

@@

\bibliographystyle{../mnras}
\bibliography{../epic} % if your bibtex file is called example.bib
